Calculating life expectancy and exploring missingness

### 2017-01-20 Code/1_Explore_Data.Rmd
change vars

```{r write_data_to_csvs}
#save.image(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
write_csv(dat.clean, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.Rdata", col_names = T)
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.Rdata", col_names = T)
```

>>>>

```{r write_data_to_csvs}
#save.image(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
write_csv(dat.clean, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.csv", col_names = T)
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.csv", col_names = T)
```
